% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Chuannan Zhang}

\basicInfo{
  \email{edwardzcn98@gmail.com} \textperiodcentered\ 
  \phone{(+86) 15630152367} \textperiodcentered\ 
  \linkedin[Edwardzcn]{https://www.linkedin.com/in/edwardzcn}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{University of Science and Technology of China (USTC)}, Hefei, China}{2021 -- Present}
\textit{M.S.} Major in Computer Science, expected June 2024
\datedsubsection{\textbf{Central South University}, Changsha, China}{2017 -- 2021}
\textit{B.S.} Major in Computer Science

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Alibaba Inc.} Hangzhou, China}{September 2022 -- April 2023}
\role{Research Intern}{Mentor: Yingqiang Zhang}
Build a geo-replicated storage system named EriaDB achieved fine-grained ownership management across multiple Paxos groups.
\begin{itemize}
  \item Implemented RPC triggered fine-grained ownership transfer protocol.
  \item Implemented sysbench-geo adapted a well-known benchmark to generate geo-distributed workload distributed by multiple clients.
\end{itemize}

\datedsubsection{\textbf{Huawei Inc.} Shanghai, China}{October 2020 -- January 2021}
\role{Research Intern}{Mentor: Xin Gao}
Assist the verification Group of OS Kernel Lab building demos demonstrating formal verification in real-world softwares.
\begin{itemize}
  \item Implemented the front-end part of Lustre V6 compiler demo using ocammllex and ocamlyacc.
  \item Learned the basic theory of formal verification and the usage of Coq.
\end{itemize}

\section{\faTasks\ Projects}
\datedsubsection{\textbf{Verification and Implementaion of Fine-grained Consensus Protocol}}{June 2023 -- Present}
Master Thesis Project

\begin{itemize}
  \item Use TLA+ to verify the correctness of a variant of Paxos protocol supporting fine-grained ownership transfer in the model layer.
  \item Implement yet another framework for testing or reasoning about the implementation of actual distributed systems using specific consensus protocol.
\end{itemize}


\datedsubsection{\textbf{Preimage attack on SHA-3}}{April 2020 -- June 2020}
\datedsubsection{Individual Projects}{URL: \href{https://github.com/Edwardzcn/KeccakAttack}{https://github.com/Edwardzcn/KeccakAttack}}

\begin{itemize}
  \item Attend the 2020 National Cryptography and Mathematic Challenge and win the second prize in the final.
  \item Use linear structures (AsiaCrypt 16) to attack the first two rounds of Keccak256 and explore a specific structure to attack the third round.
\end{itemize}




% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C, C++, Python, Rust, Java, Go
  \item Languages: English - Fluent, Mandarin - Native speaker
  \item Sports and Arts: Basketball, Trekking, Mountaineering, Photography
\end{itemize}

% \section{\faHeartO\ Honors and Awards}
% \datedline{\textit{\nth{1} Prize}, Award on xxx }{Jun. 2013}
% \datedline{Other awards}{2015}

% \section{\faInfo\ Miscellaneous}
% \begin{itemize}[parsep=0.5ex]
%   \item Blog: http://your.blog.me
%   \item GitHub: https://github.com/username
%   \item Languages: English - Fluent, Mandarin - Native speaker
% \end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
